%!TEX root = ./intern_report.tex
\section*{Preface}

\paragraph{}
This report describes my industrial training experience of 24 weeks at DATA61, CSIRO, starting from 25th June 2018 to 10th December 2018. The training programme was supervised by the by the Industrial Training Division of University of Moratuwa and NAITA. The report contains the following three chapters:

\subsubsection*{Chapter 1: Introduction to DATA61, CSIRO}
\paragraph{}
CSIRO is the federal scientific research institution of Australia. The Robotics and Automation Group of DATA61, CSIRO is a group of world class roboticists working on cutting edge technology and its application in the industry. This group is known for their state of the art SLAM technology which is used in various industries. 

\subsubsection*{Chapter 2: Training Experience}
\paragraph{}
As a research intern, I was given the task to build an end to end pipeline for machine learning in robotics and demonstrate it through two tasks of computer-vision based autonomous navigation. The work included building a robot to collect data, collecting data, storing it in the supercomputer, building the input pipeline to preprocess the data and  train a model, optimize the trained model for deployment on embedded devices and hence building navigation systems that run on those embedded devices.

\subsubsection*{Chapter 3: Conclusion}
\paragraph{}
Overall, I had an exceptional training experience thanks to NAITA and DATA61. I learnt a lot about neural network architectures, familiarized myself with machine learning tools and worked with rare resources such as the supercomputer cluster in CSIRO. I also got experience working in a research environment, etiquettes and responsibilities of working as an employee in a company. 

\newpage
\section*{Acknowledgment}

\paragraph{}
I would like to extend my gratitude towards the following persons and organizations for the successful completion of my six-month internship at DATA61, CSIRO. Firstly, I would like to thank the Department of Electronics and Telecommunications Engineering, Faculty of Engineering, University of Moratuwa, Industrial Training
Division of the University of Moratuwa and National Apprentice and Industrial Training Authority (NAITA) for
arranging and coordinating this industrial training programme. 

\paragraph{}
Next, I would like to thank Dr. Navinda Kottege (research scientist at DATA61, Brisbane), for this internship opportunity and his support and assistance prior and throughout the programme. I am also greatly indebted to my supervisor: Nicolas Hudson (research scientist at DATA61, Brisbane) for supervising my work there and sharing his knowledge and experience in Machine Learning and guiding my path.

\paragraph{}
I am also thankful to other scientists at DATA61: Micheal Thoreau, James Brett and Matt Wildie for helping and supporting me through this programme. Finally, I would like to thank my friends from Sri Lanka and the international friends I met and worked with in Brisbane for making this internship a pleasant experience.

\vspace*{3cm}

\noindent Abarajithan Gnaneswaran,\newline
Undergraduate,\newline
Department of Electronics and Telecommunication Engineering,\newline
University of Moratuwa.