%!TEX root = ./intern_report.tex

\subsection{How I got the Opportunity}

\paragraph{}
After graduation, I wanted to continue doing higher studies and become an academic, rather than settling for a job at a company. Therefore, for my internship, I applied for research opportunities in universities and institutes around the world. I got positive response from two or three institutes, one of them being CSIRO. I sent my CV to Dr. Navinda Kottege from RAG, DATA61, CSIRO in February 2018, requesting a research internship opportunity. He asked me to complete a set of 3 timed tasks online to assess my skills in programming and algorithms. He then interviewed and offered me the position as research intern student in CSIRO for 6 months.

\paragraph{}
Initially I was informed that I am being assigned to the project titled "Computer vision based off-board autonomous UAV Navigation" under the supervision of Mr. Frederick Pauling, a highly capable and friendly senior engineer in DATA61. I was informed that knowledge in ROS (Robot Operating System) and Tensorflow would be necessary, so I spent few weeks learning the basics before the internship ~\cite{mobile_cnn}.

\paragraph{}
However, when I arrived at CSIRO, Mr. Frederick Pauling had been promoted into the Group Leader of RAG (Robotics and Autonomous systems Group), to lead the cutting edge robotics research in Australia. Therefore, I could not be assigned into the said project under his supervision. As a result, Uvindu and I was assigned under the supervision of Mr. Nicolas Hudson.

\paragraph{}
Mr. Nicolas Hudson arrived CSIRO only few weeks before us, after working as a senior roboticist in NASA's Jet Propulsion Laboratory, Boston Dynamics and Google's Machine Learning Division. In CSIRO he wanted to streamline the workflow of the RAG group and incorporate Machine Learning tools into their workflow seamlessly. He asked us to work with him in one of his experimental projects: "Learning Transfer Across RGB, Thermal and IR Modalities in CNNs" ~\cite{cross_modal1} ~\cite{distill1}. After about a week, Uvindu requested for a project that is more focused on hardware. Hence, he asked us to modify Trailnet for autonomous indoor navigation.

